Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
conclusion p

In addition, this could be extended using time-aggregated networks and a
moving-window approach to inform the temporal scale including time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. 
-->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
We found increased edge overlap in fall, winter and spring (approximately October - 
June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A). 
Similarly, individual graph strength was also higher in these periods 
(Figure \@ref(fig:temp) C). These periods of increased sociality correspond 
to seasons of heterogeneous resource availability [Peigner_2019]. By explicitly 
considering the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
represented using temporal multilayer networks than aggregated networks 
[@Pereira_2020]. Evans et al. [-@Evans_2020]
observed seasonal differences in the social structure of mice 
(*Mus musculus domesticus*) related to temperature and breeding activity. 
Finally, it is crucial to include sufficient data within sampling periods or time windows
to construct robust networks [@Farine_2017; Proskurnikov_2017]. We found
variance decreased in edge overlap and multidegree across habitat layers as well
as in graph strength within habitat layers with increasing number of 
observations (Figure \@ref(fig:nobs)). As more observations were added, rarer
relationships were recorded revealing the value of this form of sensitivity
analysis.

>>>>

-->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
We found increased edge overlap and graph strength in fall, winter and spring (approximately October - 
June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A, C). 
These periods of increased sociality correspond 
to seasons of heterogeneous resource availability [Peigner_2019]. This analysis 
could be extended using time-aggregated networks and a
moving-window approach to time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. By explicitly 
considering the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
represented by temporal multilayer networks than aggregated networks 
[@Pereira_2020]. Evans et al. [-@Evans_2020]
observed seasonal differences in the social structure of mice 
(*Mus musculus domesticus*) related to temperature and breeding activity. 
Finally, it is crucial to include sufficient data within sampling periods or time windows
to construct robust networks [@Farine_2017; Proskurnikov_2017]. With increasing
number of observations, we found
variance decreased in edge overlap and multidegree across habitat layers as well
as in graph strength within habitat layers (Figure \@ref(fig:nobs)). 
As more observations were added, rarer
relationships were recorded demonstrating the value of this form of sensitivity
analysis.
